Component response rate variation drives stability in large complex systems

### 2018-06-18 notebook/SI.Rmd
Change the wording in the SI

```{r}
summarise_randmat_ga <- function(tot_res, fea_res){
    sims    <- length(tot_res);
    all_res <- matrix(data = 0, nrow = sims, ncol = 10);
    for(i in 1:sims){
        unstables <- tot_res[[i]][,1] == FALSE & tot_res[[i]][,2] == FALSE;
        stables   <- tot_res[[i]][,1] == TRUE  & tot_res[[i]][,2] == TRUE;
        unstabled <- tot_res[[i]][,1] == TRUE  & tot_res[[i]][,2] == FALSE;
        stabled   <- tot_res[[i]][,1] == FALSE & tot_res[[i]][,2] == TRUE;
        non_feas  <- fea_res[[i]][,1] == FALSE & fea_res[[i]][,2] == FALSE;
        feasibl   <- fea_res[[i]][,1] == TRUE  & fea_res[[i]][,2] == TRUE;
        unfeased  <- fea_res[[i]][,1] == TRUE  & fea_res[[i]][,2] == FALSE;
        feased    <- fea_res[[i]][,1] == FALSE & fea_res[[i]][,2] == TRUE;
        foundd    <- tot_res[[i]][,3] == TRUE;
        all_res[i, 1]  <- i + 1;
        all_res[i, 2]  <- sum(unstables);
        all_res[i, 3]  <- sum(stables);
        all_res[i, 4]  <- sum(unstabled);
        all_res[i, 5]  <- sum(stabled);
        all_res[i, 6]  <- sum(non_feas);
        all_res[i, 7]  <- sum(feasibl);
        all_res[i, 8]  <- sum(unfeased);
        all_res[i, 9]  <- sum(feased);
        all_res[i, 10] <- sum(foundd);
    }
    return(all_res);
}
```

Some stability results from this table are shown below. Results for `A0` indicate systems in which $\gamma = 1$, while `A1` refers to systems in which the genetic algorithm searched for a set of $\gamma$ values that stabilised the system.

>>>>

```{r}
summarise_randmat <- function(tot_res, fea_res){
    sims    <- length(tot_res);
    all_res <- matrix(data = 0, nrow = sims, ncol = 7);
    for(i in 1:sims){
        A0_unst   <- tot_res[[i]][,1] == FALSE;
        A0_stbl   <- tot_res[[i]][,1] == TRUE;
        A1_unst   <- tot_res[[i]][,2] == FALSE;
        A1_stbl   <- tot_res[[i]][,2] == TRUE;
        stabled   <- tot_res[[i]][,1] == FALSE & tot_res[[i]][,2] == TRUE;
        unstabled <- tot_res[[i]][,1] == TRUE  & tot_res[[i]][,2] == FALSE;
        all_res[i, 1]  <- i + 1;
        all_res[i, 2]  <- sum(A0_unst);
        all_res[i, 3]  <- sum(A0_stbl);
        all_res[i, 4]  <- sum(A1_unst);
        all_res[i, 5]  <- sum(A1_stbl);
        all_res[i, 6]  <- sum(stabled);
        all_res[i, 7]  <- sum(unstabled);
    }
    colnames(all_res) <- c("N", "A0_unstable", "A0_stable", "A1_unstable",
                           "A1_stable", "A1_stabilised", "A1_destabilised");
    return(all_res);
}
```

Stability results for 40000 $M$ for each $S$ from 2-40 are shown below. Results for `A0` indicate systems in which $\gamma = 1$, while `A1` refers to systems in which the genetic algorithm searched for a set of $\gamma$ values that stabilised the system.
